The \dealii{} Library, Version 9.4

### 2022-06-23 9.4/paper.tex
Update references for Trilinos, PETSc, Mumps, Ginkgo, GSL, CGAL, Gmesh, hdf5.
Use deal.II command for abbreviation.

In \cite{munch2022gc}, the performance of the local-smoothing and global-coarsening
infrastructure of \texttt{deal.II} was compared for locally refined meshes. The results indicate that
the local definition of multigrid levels might introduce load imbalances
in the case of local smoothing so that global coarsening is favorable despite
potentially more expensive intergrid transfers. In order to judge the benefits
of one approach against the other, \texttt{deal.II} provides new functions
\texttt{workload\_imbalance()} and \texttt{vertical\_communication\_efficiency()}
in the \texttt{MGTools} namespace for the  estimation of the imbalance during, e.g.,
smoothing and the
communication efficiency during intergrid transfer purely based on the given mesh.
% MK: I would not add this part, it does not really fit into this paper as
% there is nothing to report at this point (and we should then add references
% to the actual literature).
%The publication \cite{munch2022gc} also points out that not
%all types of smoothers are applicable for global coarsening due to the
%presence of hanging nodes, which is a motivation to add new smoother types
%to \dealii in the future.

@@

There is also a new program in the code gallery (a collection of
user-contributed programs that often solve more complicated problems
than tutorial programs, and intended as starting points for further
research rather than as teaching tools):
\begin{itemize}
  \item ``\texttt{TRBDF2-DG projection solver for the incompressible Navier--Stokes equations}'' was contributed by Giuseppe Orlando Politecnico di Milano. It shows
  how to solve the incompressible Navier--Stokes equations efficiently 
  with \texttt{deal.II}'s matrix-free DG infrastructure, multigrid, and adaptive-mesh
  refinement. Interested readers are referred to~\cite{orlando2021efficient}.
\end{itemize}
Finally, the ``\texttt{MCMC for the Laplace equation}'' code gallery
program has been updated by providing MATLAB and Python versions of
the benchmark that is implemented in this code.

>>>>

In \cite{munch2022gc}, the performance of the local-smoothing and global-coarsening
infrastructure of \dealii{} was compared for locally refined meshes. The results indicate that
the local definition of multigrid levels might introduce load imbalances
in the case of local smoothing so that global coarsening is favorable despite
potentially more expensive intergrid transfers. In order to judge the benefits
of one approach against the other, \dealii{} provides new functions
\texttt{workload\_imbalance()} and \texttt{vertical\_communication\_efficiency()}
in the \texttt{MGTools} namespace for the  estimation of the imbalance during, e.g.,
smoothing and the
communication efficiency during intergrid transfer purely based on the given mesh.
% MK: I would not add this part, it does not really fit into this paper as
% there is nothing to report at this point (and we should then add references
% to the actual literature).
%The publication \cite{munch2022gc} also points out that not
%all types of smoothers are applicable for global coarsening due to the
%presence of hanging nodes, which is a motivation to add new smoother types
%to \dealii in the future.

@@

There is also a new program in the code gallery (a collection of
user-contributed programs that often solve more complicated problems
than tutorial programs, and intended as starting points for further
research rather than as teaching tools):
\begin{itemize}
  \item ``\texttt{TRBDF2-DG projection solver for the incompressible Navier--Stokes equations}'' was contributed by Giuseppe Orlando Politecnico di Milano. It shows
  how to solve the incompressible Navier--Stokes equations efficiently 
  with \dealii{}'s matrix-free DG infrastructure, multigrid, and adaptive-mesh
  refinement. Interested readers are referred to~\cite{orlando2021efficient}.
\end{itemize}
Finally, the ``\texttt{MCMC for the Laplace equation}'' code gallery
program has been updated by providing MATLAB and Python versions of
the benchmark that is implemented in this code.
